Estimating duration in the presence of misclassification

### 2024-02-14 biology-data.tex
proofing ch 4
ch 2 now cleared by SRS

\subsection{Assessment of Transmission and Contagiousness of COVID-19 in Contacts}

@@

A sample of 500 randomly selected infection episodes (selected from the episodes used in the analyses in this thesis) have their test results shown in \cref{biology-data:fig:episodes}.
As can be seen, the number of tests within an episode, their length, and other characteristics vary greatly.
\begin{figure}
  \thisfloatpagestyle{empty}
  \vspace{-5cm}
  \makebox[\textwidth][c]{\includegraphics[height=.7\paperheight]{biology-data/STATS13734/data_viz}}
  \caption[CIS infection episodes]{%
    500 randomly selected infection episodes.
    Shown are the negative tests before and after the outermost positive tests associated with the episode.
    Red dots are negative tests, green dots are positive tests, and blue dots are void tests (where the result could not be determined; excluded from other analyses).

    This figure has been provided as management information for operational planning purposes. They are provisional estimates circulated before public release. This management information should not be shared widely and should only be used for operational planning purposes. This information is not to be used publicly and ahead of being released publicly by ONS.
  }
  \label{biology-data:fig:episodes}
\end{figure}

>>>>

\subsection{Assessment of Transmission and Contagiousness of COVID-19 in Contacts} \label{biology-data:sec:ataccc}

@@

A sample of 500 randomly selected infection episodes (selected from the episodes used in the analyses in this thesis) have their test results shown in \cref{biology-data:fig:episodes}.
As can be seen, the number of tests within an episode, their length, and other characteristics vary greatly.
\begin{figure}
  \thisfloatpagestyle{empty}
  \vspace{-5cm}
  \makebox[\textwidth][c]{\includegraphics[height=.7\paperheight]{biology-data/STATS13734/data_viz}}
  \caption[CIS infection episodes]{%
    500 randomly selected infection episodes.
    Shown are the negative tests before and after the outermost positive tests associated with the episode.
    Red dots are negative tests, green dots are positive tests, and blue dots are void tests (where the result could not be determined; excluded from other analyses).
  }
\end{figure}
